### 2020-06-11 chapters/sota.tex
Removed unecessary files

\subsection{Real-Time Stream Anomaly Detection with Hierarchical Temporal Memory}
HTM\\
point outlier, model-based, prediction\\
black-box ML algorithm\\
explain properties\\
use what authors say in their review\\

\subsection{DeepAnT}
DeepAnT\\
point outlier, model-based, prediction\\
black box DL algorithm\\
explain properties\\
use what authors say in their review\\

>>>>

\subsection{Real-Time Stream Anomaly Detection with Hierarchical Temporal Memory}
HTM
\iffalse
HTM\\
point outlier, model-based, prediction\\
black-box ML algorithm\\
explain properties\\
use what authors say in their review\\
\fi
\subsection{DeepAnT}
DeepAnT
\iffalse
DeepAnT\\
point outlier, model-based, prediction\\
black box DL algorithm\\
explain properties\\
use what authors say in their review\\
\fi
